Variation in Primary Care Prescribing in Wales due to COVID-19

### 2021-05-22 writing/paper.Rmd
Change from sample_bound to composite_sd

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Second Author"
    affiliation   : "1,2"

affiliation:
  - id            : "1"
    institution   : "Centre for Health Economics & Medicines Evaluation, Bangor University, LL55 2PZ"
  - id            : "2"
    institution   : "Institute for the Psychology of Elite Performance, Bangor University, LL55 2PZ"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

@@

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

csl               : "../references/apa.csl"
documentclass     : "apa7"
classoption       : "man"
output            : 
  - papaja::apa6_pdf
  - papaja::apa6_docx
---

```{r setup, include = FALSE}
## Packages
devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(fasster)
library(feasts)
library(furrr)
library(rebus)
library(serCymruTools)
library(papaja)

@@

## Data
differences_files <- 
  list.files("../data/differences/")
names(differences_files) <- 
  str_remove_all(differences_files, "_discreps.rds")

differences <- 
  map_dfr(.x = differences_files,
          .f = ~read_rds(paste0("../data/differences/", .x)),
          .id = "drug") %>% 
  mutate(drug = as_factor(drug)) %>% 
  select(drug, regional_unit, datename, discrepancy, med)

all_prescribing <- 
  read_csv("../data/all_prescribing.csv", col_names = c("n", "datename")) %>% 
  mutate(datename = dmy(paste(28, datename, sep = "-")),
         datename = yearmonth(datename),
         regional_unit = factor("all")) %>% 
  as_tsibble(index = datename) %>% 
  filter(datename < yearmonth(dmy("01-09-2020")))

all_prescribing_pre_cv19 <- 
  all_prescribing %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

```{r analysis-preferences}
# Seed for random number generation
set.seed(32)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = TRUE)
```

@@

* Sources of data
  * GP
  * Prescribing
  * QOF
  * WIMD
* Preparing

## Identifying changes in prescribing due to COVID-19

Identifying the effects of COVID-19 is not simple, as its effects are unprecedented and its global impact prevents us from adopting a traditional treatment and control group type design. Instead, we have used time series analysis methods to create counterfactual forecasts

To understand the changes in levels of prescribing due to COVID-19, it was first necessary for us to forecast the levels of prescribing had COVID-19 not affected Wales as a baseline. To do so, we used historic data (January 2015 to December 2020) to identify from a range of time series models, one that was good fit to the data. This was done using cross-validation to reduce the likelihood of choosing a model that was overfitted to the data.

* Given the presence of seasonal variation and existing trends in levels of prescribing, we used various time series forecasting methods to account for existing trends and seasonal variation when creating the forecasts.
* For each analysis, we created a forecast that aimed to answer the question, "What would the levels of prescribing have been if COVID-19 had not affected Wales?" We then used these forecasts to estimate the changes in levels of prescribing due to COVID-19. 
* We viewed this, somewhat complex, approach as superior to more simple approaches (e.g., carrying last years levels forward, or even using the mean of the last three years).

* We did not assume that the existing processes would be the same for all drugs or all GP practices, therefore, we investigated the fit of several different time series models to the pre-COVID data. 
* We used the `fable` [@R-fable], `fasster` [@R-fasster], and the `fable.prophet` [@R-fable.prophet] packages to conduct the time series analyses.
  * Time series linear model
  * Decomposition model
  * Seasonal naïve (with and without drift)
  * Autoregressive integrated moving average [ARIMA; @Box2015]
  * Holt-Winters Additive Model [@Chatfield1978]
  * Prophet [@Taylor2018]
  * Combination models [cf. @Thomson2019]
* Prescribing quantities log transformed and forecasts use median values to reduce bias that back transformation would introduce when using the mean
* Using Jan 2015 to Dec 2019 data, we fitted several different models and assessed their accuracy using a cross-validated process to reduce the likelihood of overfitting models to the data.
  * Started with 36 months of data, used 6-month horizon as this was the horizon we would be using for the forecasts, 3-month step (to reduce computation time) **Do we want to re-run this with 1-month?**
    * Only interested in one forecast horizon: six-months

### Model selection

* Ranked by RMSE and Winkler [@Winkler1972], then the best mean ranking model is chosen
  * RMSE is scale dependant. Is suitable for comparing models of the same data.
  * Winkler score penalises models that have observations falling outside the prediction interval, thus rewards models with narrow intervals
* This combination accounts for both the point and distributional accuracy of the forecasts

### Forecasts

* Having chosen the "best model" for each practice based on the pre-COVID data, we then used this model to forecast the level of prescribing for each practice

## Reproducability and code

We used `r cite_r("r-references.bib")` for all our analyses, functions are available in the `serCymruTools` package [@R-serCymruTools], and all other code is available at https://github.com/w-hardy/sercymru.

@@

## Counterfactual forecasts

### All prescribing

```{r all-prescribing-modelling, warning=FALSE}
plan(cluster)

all_prescribing_fable_models <- 
  all_prescribing_pre_cv19 %>% 
  mutate(datename = yearmonth(datename)) %>%
  fill_gaps() %>%
  slice(1:(n()-2), .preserve = TRUE) %>%
  stretch_tsibble(.init = 36, .step = 3) %>%
  fableModels()

all_prescribing_fable_forecasts <- 
  all_prescribing_fable_models %>%
  forecast(h = 6, point_forecast = list(.median = median))

all_prescribing_fable_fits <- 
  all_prescribing_fable_forecasts %>% 
  accuracy(all_prescribing_pre_cv19, list(RMSE = RMSE, MAE = MAE, MAPE = MAPE,
                           rmse_skill = skill_score(RMSE),
                           crps_skill = skill_score(CRPS), ACF1 = ACF1,
                           winkler = winkler_score))

all_prescribing_prophet_fits <- 
  all_prescribing_pre_cv19 %>%
  mutate(datename = yearmonth(datename)) %>%
  fill_gaps() %>%
  slice(1:(n()-2), .preserve = TRUE) %>%
  stretch_tsibble(.init = 36, .step = 3) %>%
  prophetModels() %>%
  forecast(h = 6, point_forecast = list(.median = median)) %>%
  accuracy(all_prescribing_pre_cv19, list(RMSE = RMSE, MAE = MAE, MAPE = MAPE,
                           rmse_skill = skill_score(RMSE),
                           crps_skill = skill_score(CRPS), ACF1 = ACF1,
                           winkler = winkler_score))

all_prescribing_combined_fits <- 
  bind_rows(all_prescribing_fable_fits, all_prescribing_prophet_fits) %>%
  rankModels()

all_prescribing_best_model <- 
  all_prescribing_combined_fits %>% 
  slice(1, .preserve = TRUE)

all_prescribing_covid_forecast <- 
  bind_rows(fableModels(all_prescribing_pre_cv19) %>% 
            forecast(h = "6 months"),
          prophetModels(all_prescribing_pre_cv19) %>% 
            forecast(h = "6 months")) %>% 
  as_tibble() %>% 
  filter(.model == all_prescribing_best_model$.model) %>% 
  dplyr::mutate(lb_95 = quantile(n, 0.025), lb_80 = quantile(n, 0.1), 
                med = median(n), ub_80 = quantile(n, 0.9), 
                ub_95 = quantile(n, 0.975), sd = distributional::variance(n)^2, 
                n = NULL)

plan(sequential)

@@

```{r, all-prescribing-model-accuracy-hist, fig.cap="All prescribing, model accuracy"}
p1 <- all_prescribing_combined_fits %>% 
  na.omit() %>% 
  ggplot(aes(x = reorder(.model, rank, sort), y = RMSE)) +
  geom_col()

p2 <- all_prescribing_combined_fits %>% 
  na.omit() %>% 
  ggplot(aes(x = reorder(.model, rank, sort), y = winkler)) +
  geom_col()

```{r, all-prescribing-cv-plot, fig.cap="All prescribing, best model CV fit"}
all_prescribing_best_cv_model <- 
  augment(all_prescribing_fable_models) %>% 
  as_tibble() %>% 
  filter(.model == all_prescribing_best_model$.model)

```{r, all-prescribing-forecast-plot, fig.cap="All prescribing, best model fit and forecast"}
all_prescribing %>% 
  ggplot(aes(x = datename)) +
  geom_line(aes(y = n, col = "Observed", fill = "Observed")) +
  geom_line(aes(y = med, col = "Forecast", fill = "Forecast"), 
            data = all_prescribing_covid_forecast) +
  geom_ribbon(aes(ymin = lb_80, ymax = ub_80, 
                   fill = "Forecast"), alpha = .5,
              data = all_prescribing_covid_forecast) +
  geom_line(aes(y = fitted, col = "Fitted", fill = "Fitted"), 
            data = all_prescribing_best_cv_model %>% 
              group_by(datename) %>% 
              summarise(fitted = median(.fitted, na.rm = TRUE))) +
  geom_vline(xintercept = ymd("2020-03-01"), lty = 3)
```

```{r, all-prescribing-pct-change-plot, fig.cap="Percentage difference in all prescribing"}
all_prescribing %>% 
  inner_join(all_prescribing_covid_forecast, by = "datename") %>% 
  ggplot(aes(x = datename, y = (100*n/med)-100)) +
  geom_line() +
  geom_hline(yintercept = 0, lty = 3)
```

### Specific drugs

@@

>>>>

author: 
  - name          : "Will Hardy"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Susan Murphy"
    affiliation   : "3"
  - name          : "Dyfrig Hughes"
    affiliation   : "1"
  - name          : "Daniel Hill-McManus"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Centre for Health Economics & Medicines Evaluation, Bangor University, LL55 2PZ"
  - id            : "2"
    institution   : "Institute for the Psychology of Elite Performance, Bangor University, LL55 2PZ"
  - id            : "3"
    institution   : "Betsi Cadwaladr University Health Board"

@@

header-includes:
   - \usepackage{caption}
csl               : "../references/apa.csl"
always_allow_html : true
output            : 
  - html_document

---

```{r setup, include = FALSE}
## Packages
# devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(fasster)
library(feasts)
library(furrr)
library(rebus)
library(serCymruTools)
library(knitr)
library(kableExtra)
library(geepack)
library(papaja)

@@

## Data
gp <- 
  read_rds("../data/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as.character(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

# CV model accuracies
cv_model_files <- 
  paste0("../data/gp_cv_models/", 
         list.files("../data/gp_cv_models/"))
names(cv_model_files) <- 
  cv_model_files %>% 
  str_remove_all("../data/gp_cv_models/") %>% 
  str_remove_all("_gp_cv_models.rds")

# Forecast - observed
differences_files <- 
  list.files("../data/differences/")
names(differences_files) <- 
  str_remove_all(differences_files, "_discreps.rds")

differences <- 
  map_dfr(.x = differences_files,
          .f = ~read_rds(paste0("../data/differences/", .x)),
          .id = "drug") %>% 
  mutate(drug = relevel(as_factor(drug), ref = "all_drugs"),
         sd = sd^.25)

# GP extract data
data_files <-
  paste0("../data/prescribing_data/", list.files("../data/prescribing_data")) 
names(data_files) <- 
  str_remove_all(list.files("../data/prescribing_data"), ".rds")

gp_extract <- 
  map_dfr(.x = data_files,
          .f = ~(read_rds(.x) %>% 
            filter(practice_id %in% unique(differences$regional_unit))),
          .id = "drug") 
```

```{r, analysis-preferences}
# Seed for random number generation
set.seed(32)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = TRUE)
kable_opts <- options(knitr.kable.NA = "-")
```

# Introduction

@@

```{r, figure-1, fig.cap="Data processing flow."}
include_graphics("figures/data_flow.pdf")
```

```{r, table-2}
read_rds("../data/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as.character(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>%  
  filter(year == 2020) %>% 
  select(npat, ngp, dispensing, wimd2019:flu) %>% 
  mutate(across(p_male:flu, ~.x*100)) %>% 
  psych::describe() %>% 
  select(mean, sd, median, min, max) %>% 
  kable(digits = 2)
```

@@

```{r, figure-2, fig.cap="Distribution of the difference between observed and forecast prescribing, expressed as a percentage of forecast prescribing. Grey line marks forecast level of prescribing. Pink shading covers duration of Wales' \"stay at home\" order. Please note the difference y-axis scales across the plots.", dpi=450}
differences_quantiles <- 
  differences %>% 
  na.omit() %>% 
  group_by(datename, drug) %>% 
  summarise(mean_prop = mean(prop, na.rm = T),
            med_prop = median(prop, na.rm = T),
            sd_prop = sd(prop, na.rm = T),
            se_prop = sd(prop, na.rm = T)/sqrt(length(prop)),
            enframe(quantile(prop, seq(.1,.9,.2)), 
                    "Percentile", "prop"),
            .groups = "drop") %>% 
  mutate(datename = month(datename),
         prop = 100*(prop - 1)) # Percentage change instead of proportion

differences_quantiles %>%
  mutate(datename = factor(x = datename, levels = 1:8, 
                           labels = month.abb[1:8])) %>% 
  mutate(drug = case_when(drug == "all_drugs" ~ "All",
                          drug == "ace" ~ "ACE inhibitors",
                          drug == "adreno" ~ "Adrenoceptor agonists",
                          drug == "azithro" ~ "Azithromycin",
                          drug == "contra" ~ "Oral contraceptives",
                          drug == "cortico" ~ "Corticosteroids",
                          drug == "hcq" ~ "Hydroxycholoroquine",
                          drug == "nsaid" ~ "NSAIDs",
                          drug == "paracet" ~ "Paracetamol",
                          drug == "ssri" ~ "SSRIs",
                          drug == "vitd" ~ "Vitamin D",
                          drug == "warfarin" ~ "Warfarin"),
         drug = relevel(as_factor(drug), ref = "All")) %>%
  ggplot(aes(x = datename, col = drug, 
             group = Percentile)) +
  geom_rect(aes(xmin = "Mar", xmax = "Jul", ymin = -Inf, ymax = Inf),
            fill = 'pink', col = 0,alpha = 0.03) +
  geom_line(aes(y = prop, lty = Percentile)) +
  geom_hline(aes(yintercept = 0), alpha = .5) +
  facet_wrap(~drug, scales = "free") + 
  guides(size = "legend", colour = "none") + 
  theme(legend.position = "bottom", text = element_text(size = 10)) +
  scale_linetype_manual(breaks = c("10%", "30%", "50%"), # Remove 70% and 90% from legend
                        values = c(3,2,1,2,3), # Replicate line type
                        labels = c("10% lower; 90% upper", # Amalgamate line type labels
                                   "30% lower; 70% uppper", "50%")) +
  xlab("Month") +
  ylab("Percentage difference from forecast prescribing")

  ggsave(filename = "Draft 2/Figures/Figure 2.png", device = "png",
         width = 10.5)

@@

```{r}
avg <- function(samples){
  if (length(samples) >= 1){
    return(sum(samples) / length(samples))
  }
  else{return(NaN)}
}

sample_SD <- function(samples){
  # Input is an vector of samples; result is the standard deviation
  mean = avg(samples)
  sum_of_squared_deviations <-  0
  sd <-  0
  if(length(samples) >= 2){
    for (datum in samples){
      sum_of_squared_deviations <- 
        sum_of_squared_deviations + ((datum - mean) * (datum - mean))
      sd = sqrt(sum_of_squared_deviations / (length(samples)-1))
    }
      return(sd)
  }
}

set.seed(134)
vec <- c(rnorm(n = 100), rnorm(n = 100))
vec_sd <- sd(vec)
sample_SD(vec)
compositeSD()

vec
compositeSD <- function(means, SDs, ncounts){
  #Calculate combined standard deviation via ANOVA (ANalysis Of VAriance)
  # See:  http://www.burtonsys.com/climate/composite_standard_deviations.html
  #    Inputs are:
  #      means, the array of group means
  #      SDs, the array of group standard deviations
  #      ncounts, number of samples in each group (can be scalar
  #               if all groups have same number of samples)
  #    Result is the overall standard deviation.
  G <- length(means) # number of groups
  if(G != length(SDs)) stop("Inconsistent lengths (means & sds")
  if(!is.numeric(ncounts)) {(as.numeric(ncounts))}
  if(G != length(ncounts)) stop("Inconsistent lengths (means & ncounts)")

  # Calculate total number of samples, N, and grand mean, GM
  N = sum(ncounts)  # total number of samples
  if (N <= 1) stop(paste("Warning: only ", N, " samples, SD is incalculable"))
  GM <-  0.0
  for (i in 1:G){
    GM <- GM + means[i] * ncounts[i]
  }
  GM <- GM / N  # grand mean

  # calculate Error Sum of Squares
  ESS <-  0.0
  for (i in 1:G){
    ESS <- ESS + ((SDs[i])**2) * (ncounts[i] - 1)
  }

  # calculate Total Group Sum of Squares
  TGSS <-  0.0
  for (i in 1:G){
    TGSS <- TGSS + ((means[i]-GM)**2) * ncounts[i]
  }

  # calculate standard deviation as square root of grand variance
  result <- sqrt((ESS+TGSS)/(N-1))
  return(result)
}

samples = 0:9
print(paste("avg =", avg(samples)))
sd = sample_SD(samples)
print(paste("sd =", sd))
pt1 = c(0,1,2)
pt2 = c(3,4)
pt3 = c(5,6,7,8,9)
means <- c(avg(pt1), avg(pt2), avg(pt3))
SDs <- c(sample_SD(pt1), sample_SD(pt2), sample_SD(pt3))
ncounts <- c(length(pt1), length(pt2), length(pt3))
sd2 <- compositeSD(means, SDs, ncounts)
print(paste("sd2 =", sd2))

samples = 0:8
print(paste("avg =", avg(samples)))
sd = sample_SD(samples)
print(paste("sd =", sd))
pt1 = c(0,1,2)
pt2 = c(3,4,5)
pt3 = c(6,7,8)
means <- c(avg(pt1), avg(pt2), avg(pt3))
SDs <- c(sample_SD(pt1), sample_SD(pt2), sample_SD(pt3))
ncounts <- c(length(pt1), length(pt2), length(pt3))
sd2 <- compositeSD(means, SDs, ncounts)
print(paste("sd2 =", sd2))

```{python}

from __future__ import print_function, division  # requires python 2.6 or later (2.7 or later preferred)
import math

__all__ = ['iterable', 'avg', 'sample_SD', 'composite_SD']

def iterable(obj):
    '''True iff obj is iterable: a list, tuple, or string.'''
    return hasattr(obj, '__contains__')

def avg(samples):
    if len(samples) >= 1:
        return sum(samples) / len(samples)
    return float('nan')

def sample_SD(samples):
    '''input is an array of samples; result is the standard deviation'''
    mean = avg(samples)
    sum_of_squared_deviations = 0;
    sd = 0
    if len(samples) >= 2:
        for datum in samples:
            sum_of_squared_deviations += ((datum - mean) * (datum - mean));
        sd = math.sqrt(sum_of_squared_deviations / (len(samples)-1) );
    return sd

def composite_SD(means, SDs, ncounts):
    '''Calculate combined standard deviation via ANOVA (ANalysis Of VAriance)
       See:  http://www.burtonsys.com/climate/composite_standard_deviations.html
       Inputs are:
         means, the array of group means
         SDs, the array of group standard deviations
         ncounts, number of samples in each group (can be scalar
                  if all groups have same number of samples)
       Result is the overall standard deviation.
    '''
    G = len(means)  # number of groups
    if G != len(SDs):
        raise Exception('inconsistent list lengths')
    if not iterable(ncounts):
        ncounts = [ncounts] * G  # convert scalar ncounts to array
    elif G != len(ncounts):
        raise Exception('wrong ncounts list length')

    # calculate total number of samples, N, and grand mean, GM
    N = sum(ncounts)  # total number of samples
    if N <= 1:
        raise Exception("Warning: only " + str(N) + " samples, SD is incalculable")
    GM = 0.0
    for i in range(G):
        GM += means[i] * ncounts[i]
    GM /= N  # grand mean

    # calculate Error Sum of Squares
    ESS = 0.0
    for i in range(G):
        ESS += ((SDs[i])**2) * (ncounts[i] - 1)

    # calculate Total Group Sum of Squares
    TGSS = 0.0
    for i in range(G):
        TGSS += ((means[i]-GM)**2) * ncounts[i]

    # calculate standard deviation as square root of grand variance
    result = math.sqrt((ESS+TGSS)/(N-1))
    return result

samples = range(10)
print(samples)
print('avg=', avg(samples))
sd = sample_SD(samples)
print('sd=', sd)
pt1 = [0,1,2]
pt2 = [3,4]
pt3 = [5,6,7,8,9]
means = [avg(pt1), avg(pt2), avg(pt3)]
SDs = [sample_SD(pt1), sample_SD(pt2), sample_SD(pt3)]
ncounts = [len(pt1), len(pt2), len(pt3)]
sd2 = composite_SD(means, SDs, ncounts)
print('sd2=', sd2)

samples = range(9)
print('avg=', avg(samples))
sd = sample_SD(samples)
print('sd=', sd)
pt1 = [0,1,2]
pt2 = [3,4,5]
pt3 = [6,7,8]
means = [avg(pt1), avg(pt2), avg(pt3)]
SDs = [sample_SD(pt1), sample_SD(pt2), sample_SD(pt3)]
ncounts = 3
sd2 = composite_SD(means, SDs, ncounts)
print('sd2=', sd2)
```

```{r, table-3-single-fcts}
nat_data <- 
  data_files %>% 
  map_dfr(read_rds, .id = "drug") %>% 
  group_by(drug, datename) %>% 
  summarise(n = sum(quantity), .groups = "drop")

plan(multisession)
precribing_cv_models <- 
  nat_data %>% 
  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
         regional_unit = as.factor(drug)) %>% 
  filter(datename < yearmonth(dmy("01-01-2020"))) %>% 
  as_tsibble(index = "datename", key = "regional_unit") %>% 
  serCymruTools::regionalCV(cv_dist = 8, init = 36, step = 3)
plan(sequential)

precribing_cv_models

best_model <- 
  precribing_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE)

best_mape_over_50 <- 
  best_model %>% 
  filter(MAPE > 50)

plan(cluster)
system.time(prescribing_fcsts <-
                nat_data %>% 
  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
         regional_unit = as.factor(drug)) %>% 
  filter(datename < yearmonth(dmy("01-01-2020"))) %>% 
  as_tsibble(index = "datename", key = "regional_unit") %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts())  
plan(sequential)

best_model_discrep <- 
  best_model %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(prescribing_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(                nat_data %>% 
  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
         regional_unit = as.factor(drug)) , 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - med, # observed - forecast
         prop = n / med) %>% 
  ungroup()

best_model_discrep %>% 
  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
  summarise(n = sum(n),
            sd = compositeSD(.mean, sd, rep(1,nrow(.))),
            .mean = sum(.mean)
  )

best_model_discrep %>% 
  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
  group_by(regional_unit) %>% 
  summarise(n = sum(n),
            sd = compositeSD(.mean, sd, rep(1,5)),
            .mean = sum(.mean),
            ) %>% 
  mutate(lb = .mean - 1.96*sd,
         ub = .mean + 1.96*sd,
         lb_mean_pct_change = (100 * (n - ub)/ ub),
         mean_pct_change = (100 * (n - .mean)/ .mean),
         ub_mean_pct_change = (100 * (n - lb)/ lb),
         ) %>% 
  select(regional_unit, lb_mean_pct_change, mean_pct_change, ub_mean_pct_change)
  ggplot(aes(x = regional_unit, y = mean_pct_change)) +
  geom_col() +
  geom_errorbar(aes(ymin = lb_mean_pct_change, ymax = ub_mean_pct_change))
```

```{r, table-3}
# https://stats.stackexchange.com/questions/454120/how-can-i-calculate-uncertainty-of-the-mean-of-a-set-of-samples-with-different-u

#
# An iterative procedure to estimate mean and variance from a set of 
# measurements `x` made with known measurement errors `sigma.i`.
#
var.wt <- function(x, sigma.i, thresh=1e-6, iter.max=1e4) { # Changed from values in example (1e-6, 200)
  #
  # To avoid giving undue weight to any subset, all SDs should be nonzero.
  #
  if (missing(sigma.i)) sigma.i <- rep(0, length(x)) # No measurement error
  tol <- sum(abs(x)) * 1e-16
  sigma.i[sigma.i <= 0] <- min(c(tol, sigma.i[sigma.i > 0])) / 2
  #
  # Initialize.
  #
  v <- var(x)
  n <- length(x)
  S <- mean(sigma.i^2) # Avoids recomputing this constant within the loop
  for (i in 1:iter.max) {
    w <- 1/(v + sigma.i^2); w <- w / sum(w)
    m <- sum(x * w)
    v.0 <- max(0, sum((x-m)^2 * w) * n / (n-1) - S) 
    if (v <= v.0 * (1+thresh) && v.0 <= v * (1+thresh)) break
    v <- v.0
  }
  if (i >= iter.max) warning("Maximum iteration count exceeded.")
  list(Variance=v, Mean=m, Iterations=i)
}

sample_bound <- function(mean = ".mean", variance = "sd", 
                         bound = c(.975, .5, .025), data = .){

  # The data in the question.
  #
  x <- data[[mean]]
  sigma.i <- data[[variance]]
  (s <- var.wt(x, sigma.i))
  #
  # A parametric bootstrap.
  #
  n <- length(x)
  sigma <- sqrt(s$Variance)
  mu <- s$Mean
  set.seed(17)
  X <- replicate(5e3, {
    y <- rnorm(n, mu, sigma)
    epsilon <- rnorm(n, 0, sigma.i)
    x <- y + epsilon
    var.wt(x, sigma.i)
  })
  X <- matrix(unlist(X), 3)

  return(quantile(X[2,], bound))
}

monthly_diffs <- 
  differences %>% 
  select(drug, datename, .mean, sd, n) %>% 
  na.omit() %>% 
  group_by(drug, datename) %>% 
  group_modify(~ {
    sample_bound(data = .x) %>% # Estimate the mean and 95% CIs for each month
      tibble::enframe(name = "bound", value = "value")
  }) %>% 
  left_join(differences %>% 
              select(drug, datename, .mean, sd, n) %>% 
              na.omit() %>% 
              group_by(drug, datename) %>% 
              summarise(n = mean(n, na.rm = TRUE),
                        .mean = mean(.mean, na.rm = TRUE),
                        .group = "drop"), 
            by = c("drug", "datename")) %>% 
  mutate(p_change = 100*n / value) %>% # Difference as a proportion
  pivot_wider(id_cols = c("drug", "datename", "n", ".mean"), 
              names_from = "bound", values_from ="value") %>% 
  mutate(across(`97.5%`:`2.5%`, .fns = ~(100*n/.x)-100)) %>% # Proportion as percentage change
  rename("LB" = `97.5%`,
         "Mean" = `50%`,
         "UB" = `2.5%`) %>% 
  mutate(datename = month(datename),
         pct_change = paste0(printnum(Mean), 
                             "[", printnum(LB), ",", printnum(UB), "]"))

lockdown_diff_bounds <- 
  differences %>% 
  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
  select(drug, datename, .mean, sd, n) %>% 
  na.omit() %>% 
  group_by(drug) %>% 
  group_modify(~ {
    sample_bound(data = .x) %>% # Estimate the mean and 95% CIs for each month
      tibble::enframe(name = "bound", value = "value")
  })

lockdown_diff_bounds_wide <- 
  lockdown_diff_bounds %>% 
  pivot_wider(id_cols = "drug", names_from = "bound", values_from = "value") %>% 
  rename("lb" = `97.5%`,
         "mean" = `50%`,
         "ub" = `2.5%`) # returns mean quantity forecast per month in lockdown

lockdown_diff_obs <- 
  differences %>% 
  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
  select(drug, datename, .mean, sd, n, med) %>% 
  na.omit() %>% 
  group_by(drug) %>% 
  summarise(n = mean(n, na.rm = FALSE),
            .mean = mean(.mean, na.rm = FALSE),
            med_med = median(med),
            mean_med = mean(med),
            .groups = "drop")

left_join(lockdown_diff_obs, lockdown_diff_bounds_wide) %>% 
  mutate(across(.mean:ub, ~(n-.x)/.x))

###
lockdown_diffs <- 
  differences %>% 
  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
  select(drug, datename, .mean, sd, n) %>% 
  na.omit() %>% 
  group_by(drug) %>% 
  group_modify(~ {
    sample_bound(data = .x) %>% # Estimate the mean and 95% CIs for each month
      tibble::enframe(name = "bound", value = "value")
  }) %>% 
  left_join(differences %>% 
              filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
              select(drug, datename, .mean, sd, n) %>% 
              na.omit() %>% 
              group_by(drug) %>% 
              summarise(n = mean(n, na.rm = TRUE),
                        .mean = mean(.mean, na.rm = TRUE),
                        .groups = "drop"), 
            by = c("drug")) %>% 
  mutate(p_change = 100 * n / value) %>% # Difference as a proportion
  pivot_wider(id_cols = c("drug", "n", ".mean"), 
              names_from = "bound", values_from ="value") %>% 
  mutate(across(`97.5%`:`2.5%`, .fns = ~(100*n/.x)-100)) %>% # Proportion as percentage change
  rename("LB" = `97.5%`,
         "Mean" = `50%`,
         "UB" = `2.5%`) %>% 
    mutate(lockdown = paste0(printnum(Mean), 
                             "[", printnum(LB), ",", printnum(UB), "]"))

lockdown_diffs %>% 
  select(drug, lockdown) %>% 
  left_join(monthly_diffs %>% 
              pivot_wider(id_cols = "drug", names_from = "datename", 
                          values_from = "pct_change"), by = "drug") %>% 
  kable(col.names = c("Drug", "Lockdown", month.abb[1:8]),
        align = "lrrrrrrrrr",
        booktabs = TRUE,
        caption = "Monthly percentage change in prescribing") %>% 
  add_header_above(header = c(" " = 1, 
                              "Mean percentage change [95% CI]" = 9)) %>% 
  landscape()
```

```{r}
differences %>% 
  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
  group_by(drug) %>% 
  summarise(n = sum(n),
            .mean = sum(.mean)) %>% 
  mutate(pct_change = 100 * (n - .mean ) / .mean)
```

```{r, eval=FALSE}
differences %>% 
  select(drug, datename, .mean, sd, n) %>% 
  na.omit() %>% 
  group_by(drug) %>% 
  summarise(across(where(is.numeric),.fns = max))
```

```{r}
gp_extract %>% 
  filter(str_detect(datename, "-19")) %>% 
  group_by(drug) %>% 
  summarise(n = sum(quantity)/1e6) %>% 
  left_join(lockdown_diffs %>% 
  select(drug, lockdown), by = "drug")
```

```{r, mean-change-plot}
monthly_diffs %>% 
  ggplot(aes(x = datename, group = drug)) +
  geom_line(aes(y = Mean)) +
  geom_ribbon(aes(ymin = LB, ymax = UB, fill = drug), alpha = .4) +
  facet_wrap(~drug, scales = "free")

```{r}
differences %>% 
  group_by(drug) %>% 
  summarise(discrepancy = sum(discrepancy, na.rm = TRUE),
            n = sum(n, na.rm = TRUE),
            pct = 100*discrepancy / n)

differences %>% 
  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
  group_by(drug) %>% 
  summarise(discrepancy = sum(discrepancy, na.rm = TRUE),
            n = sum(n, na.rm = TRUE),
            pct = 100*discrepancy / n) %>% 
  ggplot(aes(x = reorder(drug, pct), y = pct)) +
  geom_col()
```

@@

<div custom-style='Title'>Appendix </div>

\renewcommand{\appendixname}{Supplementary Material}
\renewcommand{\thefigure}{SI\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{SI\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{SI\arabic{table}} \setcounter{equation}{0}

# Forecasting
